An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-28 VLDB2026/main.tex
Update main.tex

	% \begin{figure*}[htbp]
		%     \centering
		%     \setlength{\abovecaptionskip}{0cm}
		%     \setlength{\belowcaptionskip}{-0.4cm}
		%     \includesvg[width=\textwidth]{figures/exp/exp_8_3.svg}
		%     \caption{Dataset Effect on RF-ANN Search}
		%     \label{fig:exp_8_3}
		% \end{figure*}
	\begin{figure*}[htbp]
		\centering
		    \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=0.75\textwidth]{figures/exp/exp_8_3.pdf}
		\caption{Dataset Effect on RF-ANN Search}
		\label{fig:exp_8_3}
	\end{figure*}

@@

	\begin{table}[t]
		\centering
		\setlength{\abovecaptionskip}{0.0cm}
		\caption{Algorithm Recommendation per Scenario}
		\resizebox{\columnwidth}{!}{
			\begin{tabular}{|l|c|c|}
				\hline
				\textbf{Scenario} & \textbf{Attribute Filtering} & \textbf{Range Filtering}\\
				\hline
				S1: Large-scale Datasets & Puck, UNG & iRange\\
				\hline
				S2: Fast Index Construction & ACORN-1, UNG  &Faiss\\
				\hline
				S3: Query on Hard Datasets & CAPS, UNG &WinFilter, iRange, DSG\\
				\hline
				S4: Query on Easy Datasets & StitchedVamana, NHQ, UNG & WinFilter, iRange\\

				\hline
				S5: General-purpose Use & Milvus, Faiss &DSG, UNIFY\\
				\hline
				S6: Resource constraint& CAPS, Faiss&Faiss, SeRF \\
				\hline
				S7: High-Recall Querying & UNG & WinFilter \\
				\hline
				S8: OOD scenarios & UNG &WinFilter  \\
				\hline
			\end{tabular}
		}
		\label{tab:algo_scenarios}
	\vspace{-0.0cm}
	\end{table}

>>>>

	% \begin{figure*}[htbp]
		%     \centering
		%     \setlength{\abovecaptionskip}{0cm}
		%     \setlength{\belowcaptionskip}{-0.4cm}
		%     \includesvg[width=\textwidth]{figures/exp/exp_8_3.svg}
		%     \caption{Dataset Effect on RF-ANN Search}
		%     \label{fig:exp_8_3}
		% \end{figure*}
	\begin{figure*}[htbp]
		\centering
		    \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=0.80\textwidth]{figures/exp/exp_8_3.pdf}
		\caption{Dataset Effect on RF-ANN Search}
		\label{fig:exp_8_3}
	\end{figure*}

@@

	\begin{table}[t]
		\centering
		\setlength{\abovecaptionskip}{0.0cm}
		\caption{Algorithm Recommendation per Scenario}
		\resizebox{\columnwidth}{!}{
			\begin{tabular}{|l|c|c|}
				\hline
				\textbf{Scenario} & \textbf{Attribute Filtering} & \textbf{Range Filtering}\\
				\hline
				S1: Large-scale Datasets & Puck, UNG & iRange\\[1pt]
				\hline
				S2: Fast Index Construction & ACORN-1, UNG  &Faiss\\[1pt]
				\hline
				S3: Query on Hard Datasets & CAPS, UNG &WinFilter, iRange, DSG\\[1pt]
				\hline
				S4: Query on Easy Datasets & StitchedVamana, NHQ, UNG & WinFilter, iRange\\[1pt]

				\hline
				S5: General-purpose Use & Milvus, Faiss &DSG, UNIFY\\[1pt]
				\hline
				S6: Resource constraint& CAPS, Faiss&Faiss, SeRF \\[1pt]
				\hline
				S7: High-Recall Querying & UNG & WinFilter \\[1pt]
				\hline
				S8: OOD scenarios & UNG &WinFilter  \\[1pt]
				\hline
			\end{tabular}
		}
		\label{tab:algo_scenarios}
	\vspace{-0.0cm}
	\end{table}
